STR: Seasonal-Trend decomposition using Regression

### 2021-03-29 Response_to_reviewers.Rmd

- “Does it work?” When we read a new research contribution, we often ask ourselves “does this method work?” That is, we ask ourselves that, while the authors propose a new method to recover underlying or hidden time series components, does the method really uncover all of the components hidden in the data? In this paper, the authors provide some empirical examples, but they do not really answer the question of whether all the time series components, of e.g. the electricity demand in Victoria, have been truly recovered. What if there are additional components that are hiding inside the data (which the method could not detect)? In order to address this question, the referee suggests the use of simulations. Simulations are a great tool to investigate what-if questions (e.g. what if we added an hourly or minutely component to the data? Would the method then still work? What if we added more noise to the data? Or unobservable factors?) I would strongly recommend the authors consider the referee’s suggestion and see if a simulation experiment could be added to the paper.

> As suggested, we have added some simulation experiments to demonstrate our proposed method. These appear in Section 3.

- “Does it work better?” Another question we often ask ourselves is the “so what” question. Or more specifically, we ask if the proposed method, while elegant and convincing, really adds any practical value. In other words, does it work better than any of the existing methods? In the empirical examples, while the authors show the performance of STR, they do not show us how poorly (or how competitively) other benchmark methods perform. The authors argue that none of the existing methods satisfy all of the requirements of STR; however, I agree with the referee that it would add tremendous value if some benchmarking could be added to the empirical applications. That would help the reader better understand how much better STR performs (and when it performs better).

> We have now included some comparison methods in the simulations, demonstrating that our approach consistently and significantly outperforms competitor methods. We have also included some more details the first real data example in the appendix.

@@

- Special cases: It appears that a very special case of the model would be a linear regression model with a linear trend and seasonal dummy variables (plus covariates). I think it would have tremendous value for the reader if the authors could discuss special cases of their model and how they relate to the standard statistics and economics tool sets.

> Yes, that is correct. We have added two paragraphs describing some special cases --- one at the end of Section 2.1 describing a linear trend, and one at the end of Section 2.2 describing periodic seasonality.

@@

- Applications within data science: One way to look at this method of time series decomposition is in terms of feature engineering. The authors’ model provides a way for the data science researcher to identify new features in the data (such as weekly or daily patterns). Could these features then be used inside other data science methods (e.g. could the uncovered weekly or daily pattern be used as an input for a classification or forecasting model)? I think it would provide tremendous value for the data science community if the authors could discuss the application of their model/method within the wider context of data science tasks.

> We have now added this use-case in the discussion section.

@@

# Reviewer

General Assessment: The paper is very well written, well organized, and easy to follow. I believe the proposed method to be of interest to the target audience of the IJDS. However, I think the paper presents a few loose ends. Let me elaborate with a bullet-point style to facilitate the authors' evaluation.

1) Identification: I don't think the authors are convincing the reader whether the proposed method can recover unbiased parameters. I suggest the authors include extensive simulation results, either in the main text or in a supplementary appendix. Using simulations would also help assess what kind of "richness" in the data is needed to correctly estimate the model; this is an essential requirement for a data science paper.

> We have now added simulations in Section 3 showing that our method consistently and significantly outperforms the only competitors available for multiple-seasonal decomposition.

@@

2) Benchmarking: the authors should include potential alternative (traditional STR method) or multiscale/wavelet alike (See Zhang et al. 2017 for a quick reference and potential suggestion) method and compare the predictive performance across them.

> We have now compared our approach against STL and TBATS in the simulations, and against STL, TBATS and X-13-ARIMA-SEATS in the appendix. It would be difficult to compare against the approach proposed by Zhang et al (2017) as their decomposition does not contain explicit trend or remainder terms, and the multiple seasonal terms do not match those in other formulations of time series decomposition. Further, the authors do not provide any open-source implementation of their approach.

@@

3) I suggest the authors consider an additional dataset that could make the paper more appealing to a vaster audience. As a suggestion, the authors could consider time series extracted from Google Trends about Covid (https://trends.google.com/trends/story/US_cu_4Rjdh3ABAABMHM_en)

> We have included two real examples, one with monthly data of the kind that official statistics agencies need to deal with, and one with sub-daily data showing the richness of our method in an application that existing methods are incapable of handling. We do not think that a further example will make the paper any more appealing. Data from Google Trends about Covid would certainly be a plausible application, but it would not show anything that we have not already demonstrated.

@@

4) I enjoyed reading the extended yet brief discussion in Section 4. I think that 4.2 could be implemented in the main paper to make a more substantial methodological contribution. It would be indeed intriguing to see how the bias/variance trade-off obtained using different regularizers (or a combination thereof) can impact the results' quality.

> An earlier version of the paper did contain some additional material on robust regularization, but it led to the paper being too long for the journal, and we feel that there is enough methodological innovation without adding alternative regularization as well.

### 2021-03-29 str_ijds.Rmd
Nearly ready to resubmit

---
title: "STR: Seasonal-Trend decomposition using Regression"
author:
 - familyname: Dokumentov
   othernames: Alexander
   address: Growing Data\newline Australia
 - familyname: Hyndman
   othernames: Rob J
   address: Monash University\newline Australia
   email: Rob.Hyndman@monash.edu
   correspondingauthor: true
abstract: "We propose a new method for decomposing seasonal data: STR (a Seasonal-Trend decomposition using Regression). Unlike other decomposition methods, STR allows for multiple seasonal and cyclic components, covariates, seasonal patterns that may have non-integer periods, and seasonality with complex topology. It can be used for time series with any regular time index including hourly, daily, weekly, monthly or quarterly data. It is competitive with existing methods when they exist, but tackles many more decomposition problem than other methods allow.\\par STR is based on a regularized optimization, and so is somewhat related to ridge regression. Because it is based on a statistical model, we can easily compute confidence intervals for components, something that is not possible with most existing decomposition methods (such as STL, X-12-ARIMA, SEATS-TRAMO, etc.).\\par
  Our model is implemented in the R package *stR*, so can be applied by anyone  to their own data."
keywords: "time series decomposition, seasonal data, Tikhonov regularisation, ridge regression, LASSO, STL, TBATS, X-12-ARIMA, BSM"
blind: false
cover: false
toc: false
bibliography: strrefs.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: no
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \graphicspath{{figs/}}
  - \usepackage{amsmath}
  - \setlength{\arraycolsep}{3pt}
  - \setcounter{MaxMatrixCols}{20}
  - \newcommand{\argmin}{\operatorname{arg\,min}}
  - \newcommand{\sn}{\kappa}
  - \renewcommand{\vec}{\operatorname{vec}}
  - \newcommand{\diag}{\operatorname{diag}}
  - \renewcommand{\mod}{\operatorname{mod}}
  - \usepackage[section]{placeins}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE
)
library(tidyverse)
library(stR)
library(fabletools)
library(distributional)
library(lubridate)
library(knitr)
library(kableExtra)
set.seed(2020 - 03 - 28)

# Create predictor dist object
predictor_dist <- function(x, level) {
  dist_percentile(
    with(x, mapply(c, data, split(lower, row(lower)), split(upper, row(upper)), SIMPLIFY = FALSE)),
    list(c(50, 50 + rep(c(-1, 1), each = length(level)) * rep(level, 2) / 2))
  )
}

source("simulations.R")
```

@@

The first attempts to decompose time series into various components can be dated to the 19th century, when @Poynting1884 proposed price averaging as a tool for eliminating trend and seasonal fluctuations. Later, his approach was extended by @hooker1901suspension, @spencer1904graduation and @anderson1914nochmals. Further research in this direction included that by @copeland1915statistical, who was the first to attempt to extract the seasonal component, until @macaulay1930smooth proposed a method which gradually became "classical". The work of Macaulay led to the Census II method [@shiskin1957electronic] which became popular amongst national statistics offices. The Census II method has continued to evolve, with additional features including robustness, calendar effects, covariates, ARIMA extensions, and extensive diagnostics. Widely used versions of this approach have been X-11 [@shishkin1967x], X-11-ARIMA [@dagum1988x11arima;@ladiray2001seasonal], X-12-ARIMA [@findley1998new] and X-13-ARIMA-SEATS [@findley2005some].

@@

Several model-based methods for seasonal decomposition have been developed, including the TRAMO/SEATS procedure which was developed at the Bank of Spain [@Gomez2001], the TBATS model of @de2011forecasting, and various structural time series model approaches [@harvey1990forecasting;@Commandeur2011]. One big advantage of using a model for seasonal decomposition and adjustment is that it provides a natural way to compute confidence and prediction intervals.

@@

@@

@@

\begin{figure}
  \centering
  \centerline{Working day \hspace*{4.5cm} Holiday}
  \includegraphics[width=0.6\textwidth]{topology.pdf}
  \caption{Topology of the complex seasonality modelling human behaviour during working days, holidays and transition periods.}
  \label{fig:topology_pdf}
\end{figure}

@@

To demonstrate that our method estimates the appropriate time series components, we use simulations where we know the true underlying components. We will compare our results against two other decomposition methods that handle multiple seasonal components, STL and TBATS. STL [@cleveland1990stl] is a well known decomposition method, and therefore a natural choice to use as a method to compare. The original methodology and implementation was designed for only one seasonal period. However, the implementation in the forecast package for R [@Rforecast] will compute an STL decomposition iteratively with multiple seasonal periods. TBATS [@de2011forecasting] is a forecasting method designed for multiple seasonalities; it provides a decomposition of the time series into components, and so can provide an alternative comparison.

@@

Figure \@ref(fig:examples) shows examples of simulated time series from each of the two DGPs with $\alpha=\beta=1$ and $\gamma=0.25$. We generated 1095 days in each case (three non-leap years of daily data).

```{r examples, fig.cap="Examples of time series generated by the two DGPs.", fig.height=3.5}
bind_rows(
  get_msts_data(type = "stochastic", l = 1095, gamma=.4) %>% 
    mutate(type = "Stochastic", day = row_number()),
  get_msts_data(type = "deterministic", l = 1095, gamma=.4) %>% 
     mutate(type = "Deterministic", day = row_number())
) %>%
  ggplot(aes(x = day, y = data, group = type)) +
  geom_line() +
  facet_grid(type ~ .)
```

For comparison of STR, STL and TBATS we use parameter sets $(\alpha, \beta, \gamma) = \{(1, 1, 0.2), (1, 1, 0.4), (1, 1, 0.6)\}$, and create 20 time series for each DGP and parameter set. We apply STR, STL and TBATS to each series and compute MSE for each component (averaging across all data sets). The results are shown in Table \@ref(tab:cbetable). It is clear that STR outperforms STL and TBATS in these scenarios.

```{r errors}
n <- 100
errors <- bind_rows(
  compute_n_errors(n = n, gamma = 0.2, type = "stochastic"),
  compute_n_errors(n = n, gamma = 0.4, type = "stochastic"),
  compute_n_errors(n = n, gamma = 0.6, type = "stochastic"),
  compute_n_errors(n = n, gamma = 0.2, type = "deterministic"),
  compute_n_errors(n = n, gamma = 0.4, type = "deterministic"),
  compute_n_errors(n = n, gamma = 0.6, type = "deterministic")
)
```

```{r signif}
errors <- errors %>%
       mutate(method = factor(method, c("STR","STL","TBATS")))

pvalues <- bind_rows(
    get_pvalues(errors, type="stochastic", gamma=0.2),
    get_pvalues(errors, type="stochastic", gamma=0.4),
    get_pvalues(errors, type="stochastic", gamma=0.6),
    get_pvalues(errors, type="deterministic", gamma=0.2),
    get_pvalues(errors, type="deterministic", gamma=0.4),
    get_pvalues(errors, type="deterministic", gamma=0.6)
  ) %>%
  mutate(method = str_remove(term,"method")) %>%
  select(-term) 
```

```{r cbetable}
rmse <- errors %>%
  group_by(type, gamma, method) %>%
  summarise(
    trend = sqrt(mean(trend^2)),
    season_week = sqrt(mean(season_week^2)),
    season_year = sqrt(mean(season_year^2)),
    remainder = sqrt(mean(remainder^2)),
  ) %>%
  ungroup()
rmse %>%
  pivot_longer(trend:remainder, names_to="var", values_to="rmse") %>%
  left_join(pvalues, by=c("type","gamma","method","var")) %>%
  mutate(
    method = factor(method, levels = c("STL","TBATS","STR")),
    rmse = sprintf("%.4f", rmse),
    rmse = if_else(p.value < 0.05, paste0("\\textbf{",rmse,"}"), rmse, missing=rmse)
  ) %>%
  pivot_wider(c(type,gamma,method),names_from="var",values_from="rmse") %>%
  arrange(type,gamma,method) %>%
  select(gamma, method, everything(), -type) %>%
  knitr::kable(
    col.names = c("$\\gamma$", "Method", "Trend RMSE", "Weekly RMSE", "Yearly RMSE", "Remainder RMSE"),
    caption = "RMSE over 100 simulations for each DGP and value of $\\gamma$. Bold values indicate results that are significantly different from the STR values.",
    digits = 3,
    escape = FALSE,
    align = "rlrrrr",
    booktabs = TRUE,
    format = "latex",
    table.envir = "table",
    position = "!ht"
  ) %>%
  kable_styling() %>%
  pack_rows("Stochastic DGP", 1, 9) %>%
  pack_rows("Deterministic GDP", 10, 18) %>%
  row_spec(seq(3, 15, by = 3), extra_latex_after = "\\midrule")
```

@@

We obtained similar results using other decomposition methods applied to the same data including STL [@cleveland1990stl] and X-13-ARIMA-SEATS [@findley2005some].

@@

```{r vic, fig.height=10, fig.cap="Electricity demand in Victoria, decomposed using STR. The original data are plotted in black in the first panel, with the decomposed trend plotted in red. The subsequent panels contain the weekly seasonal pattern; the daily seasonal pattern with complex topology; the effect of temperature in Melbourne, which has a daily seasonal pattern with complex topology; the effect of squared temperatures in Melbourne, which is allowed to vary over time; and the residuals. Grey vertical lines represent the residuals with the largest absolute values.", dependson='outliers'}
elec_dbl <- elec %>%
  as_tsibble(index = DateTime) %>%
  mutate(
    Remainder = elec_str$output$random$data,
    Trend = predictor_dist(elec_str$output$predictors[[1]], 95),
    Weekly = predictor_dist(elec_str$output$predictors[[2]], 95),
    Daily = predictor_dist(elec_str$output$predictors[[3]], 95),
    Temp = predictor_dist(elec_str$output$predictors[[4]], 95),
    Tempsq = predictor_dist(elec_str$output$predictors[[5]], 95),
  ) %>%
  select(DateTime, Demand, Trend, Weekly, Daily, Temp, Tempsq, Remainder) %>%
  as_dable(
    response = "Demand",
    aliases = rlang::exprs(Demand = Trend + Weekly + Daily + Temp + Tempsq + Remainder),
    method = "STR"
  )

p <- elec_dbl %>%
  autoplot(size = 0.5, fill = "blue", level = 95) +
  xlab("Month") +
  geom_vline(data = outliers, aes(xintercept = DateTime), col = "gray") +
  ggplot2::theme_bw() + theme(legend.position = "none")
# Put vline behind data
p$layers <- p$layers[c(1, 4, 2, 3)]
p
```

@@

```{r outlierstable, results='asis'}
outliers %>%
  mutate(
    Hour1 = hour(DateTime),
    Hour2 = hour(DateTime + 1800),
    Minute1 = minute(DateTime) %>% as.character(),
    Minute2 = minute(DateTime + 1800) %>% as.character(),
    Minute1 = if_else(Minute1 == "0", "00", Minute1),
    Minute2 = if_else(Minute2 == "0", "00", Minute2),
    Time = paste0(Hour1, ":", Minute1, " -- ", Hour2, ":", Minute2),
    Weekday = case_when(
      Weekday == "Thu" ~ "Thursday",
      Weekday == "Fri" ~ "Friday"
    ),
    Date = paste(day(Date), month(Date, label = TRUE, abbr = FALSE), year(Date)),
  ) %>%
  select(Date, Weekday, Time, res) %>%
  knitr::kable(
    format='latex',
    col.names = c("Date", "Day of week", "Time period", "Residual"),
    digits = 1, align = "rlcr", booktabs = TRUE, linesep=10,
    caption = "The ten residuals that are largest in absolute value after an STR decomposition."
  )
```

```{r MelTemp, dependson='outliers', fig.height=3, fig.cap="The temperature in Melbourne on 1 February 2000, and the following ten days. Ten red lines (two groups of five lines each) mark the times of the outliers. The first group spans 14:30--17:00 on 3 February, while the second group spans 15:30--18:00 on the following day."}
elec %>%
  filter(Date >= "2000-02-01", Date <= "2000-02-11") %>%
  ggplot(aes(x = DateTime, y = Temp)) +
  geom_line() +
  geom_vline(data = outliers, aes(xintercept = DateTime), col = "red") +
  labs(y = "Temperature", x = "Date") +
  ggplot2::theme_bw()
```

@@

Similarly, seasonal functional components can be obtained, using Fourier terms for example [reminiscent of @de2011forecasting]. This approach leads, with no additional effort, to handling seasonality with a fractional or varying period.

@@

>>>>

---
title: "STR: Seasonal-Trend decomposition using Regression"
author:
 - familyname: Dokumentov
   othernames: Alexander
   address: Let's Forecast\newline Australia
 - familyname: Hyndman
   othernames: Rob J
   address: Monash University\newline Australia
   email: Rob.Hyndman@monash.edu
   correspondingauthor: true
abstract: "We propose a new method for decomposing seasonal data: STR (a Seasonal-Trend decomposition using Regression). Unlike other decomposition methods, STR allows for multiple seasonal and cyclic components, covariates, seasonal patterns that may have non-integer periods, and seasonality with complex topology. It can be used for time series with any regular time index including hourly, daily, weekly, monthly or quarterly data. It is competitive with existing methods when they exist, but tackles many more decomposition problem than other methods allow.\\par STR is based on a regularized optimization, and so is somewhat related to ridge regression. Because it is based on a statistical model, we can easily compute confidence intervals for components, something that is not possible with most existing decomposition methods (such as STL, X-12-ARIMA, SEATS-TRAMO, etc.).\\par
  Our model is implemented in the R package *stR*, so can be applied by anyone  to their own data."
keywords: "time series decomposition, seasonal data, Tikhonov regularisation, ridge regression, LASSO, STL, TBATS, X-12-ARIMA, BSM"
blind: false
cover: false
toc: false
bibliography: strrefs.bib
biblio-style: authoryear-comp
output:
  MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    toc: no
    keep_tex: yes
    number_sections: yes
    citation_package: biblatex
header-includes:
  - \graphicspath{{figs/}}
  - \usepackage{amsmath,pdfpages}
  - \setlength{\arraycolsep}{3pt}
  - \setcounter{MaxMatrixCols}{20}
  - \newcommand{\argmin}{\operatorname{arg\,min}}
  - \newcommand{\sn}{\kappa}
  - \renewcommand{\vec}{\operatorname{vec}}
  - \newcommand{\diag}{\operatorname{diag}}
  - \renewcommand{\mod}{\operatorname{mod}}
  - \usepackage[section]{placeins}
  - \makeatletter\let\ftype@table\ftype@figure\makeatother
include-after: 
  - \includepdf[pages=-]{str_ijds_appendix.pdf}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  cache = TRUE
)

library(tidyverse)
library(stR)
library(fabletools)
library(distributional)
library(lubridate)
library(knitr)
library(kableExtra)
set.seed(2020-03-28)

# Create predictor dist object
predictor_dist <- function(x, level) {
  dist_percentile(
    with(x, mapply(c, data, split(lower, row(lower)), split(upper, row(upper)), SIMPLIFY = FALSE)),
    list(c(50, 50 + rep(c(-1, 1), each = length(level)) * rep(level, 2) / 2))
  )
}
# Functions for generating simulations
source("simulations.R")
```

@@

The first attempts to decompose time series into various components can be dated to the 19th century, when @Poynting1884 proposed price averaging as a tool for eliminating trend and seasonal fluctuations. Later, his approach was extended by @hooker1901suspension, @spencer1904graduation and @anderson1914nochmals. Further research in this direction included that by @copeland1915statistical, who was the first to attempt to extract the seasonal component, until @macaulay1930smooth proposed a method which gradually became "classical". The work of Macaulay led to the Census II method [@shiskin1957electronic] which became popular amongst national statistics offices. The Census II method has continued to evolve, with additional features including robustness, calendar effects, covariates, ARIMA extensions, and extensive diagnostics. Widely used versions of this approach have been X-11 [@shishkin1967x], X-11-ARIMA [@dagum1988x11arima;@ladiray2001seasonal], X-12-ARIMA [@findley1998new] and X-13-ARIMA-SEATS [@findley2005some;@Dagum2016].

@@

Several model-based methods for seasonal decomposition have been developed, including the TRAMO/SEATS procedure which was developed at the Bank of Spain [@Gomez2001], the TBATS model of @delivera2011forecasting, and various structural time series model approaches [@harvey1990forecasting;@Commandeur2011]. One big advantage of using a model for seasonal decomposition and adjustment is that it provides a natural way to compute confidence and prediction intervals.

@@

Note that the model subsumes the case of a linear trend, obtained when $\sigma_L^2=0$.

@@

Again, by setting the smoothing parameters to zero, some simple special cases are obtained. Setting $\sigma_i$ to zero eliminates the $i$th seasonal component (as it will be equal to zero); setting the variance in the time direction to zero causes the seasonal component to be periodic; setting the variance in the time-season direction to zero causes ????.

@@

\begin{figure}[!hbt]
  \centering
  \centerline{Working day \hspace*{4.5cm} Holiday}
  \includegraphics[width=0.6\textwidth]{topology.pdf}
  \caption{Topology of the complex seasonality modelling human behaviour during working days, holidays and transition periods.}
  \label{fig:topology_pdf}
\end{figure}

@@

To demonstrate that our method estimates the appropriate time series components, we use simulations where we know the true underlying components. We will compare our results against two other decomposition methods that handle multiple seasonal components, STL and TBATS. STL [@cleveland1990stl] is a well known decomposition method, and therefore a natural choice to use as a method to compare. The original methodology and implementation was designed for only one seasonal period. However, the implementation in the forecast package for R [@Rforecast] will compute an STL decomposition iteratively with multiple seasonal periods. TBATS [@delivera2011forecasting] is a forecasting method designed for multiple seasonalities; it provides a decomposition of the time series into components, and so can provide an alternative comparison.

@@

Figure \@ref(fig:examples) shows examples of simulated time series from each of the two DGPs with $\alpha=\beta=1$ and $\gamma=0.25$. We generated 1096 days in each case (one day more than three non-leap years of daily data).

```{r examples, fig.cap="Examples of time series generated by the two DGPs.", fig.height=3.5}
bind_rows(
  get_msts_data(type = "stochastic", l = 1096, gamma=.4) %>% 
    mutate(type = "Stochastic", day = row_number()),
  get_msts_data(type = "deterministic", l = 1096, gamma=.4) %>% 
     mutate(type = "Deterministic", day = row_number())
) %>%
  ggplot(aes(x = day, y = data, group = type)) +
  geom_line() +
  facet_grid(type ~ .)
```

For comparison of the three decomposition methods, we use parameter sets $(\alpha, \beta, \gamma) = \{(1, 1, 0.2), (1, 1, 0.4), (1, 1, 0.6)\}$, and create 20 time series for each DGP and parameter set. We apply STR, STL and TBATS to each series and compute RMSE for each component (averaging across all data sets and days). We measure the significance of the differences between the methods using a linear model applied to the squared errors. The results are shown in Table \@ref(tab:cbetable). It is clear that STR outperforms STL in estimating all components other than the trend, and that STR outperforms TBATS in estimating all components other than the weekly seasonal pattern. In no case do the other methods outperform STR.

```{r errors}
if(fs::file_exists(here::here("errors.rds"))) {
  errors <- readr::read_rds(here::here("errors.rds"))
} else {
  n <- 100
  errors <- bind_rows(
    compute_n_errors(n = n, gamma = 0.2, type = "stochastic"),
    compute_n_errors(n = n, gamma = 0.4, type = "stochastic"),
    compute_n_errors(n = n, gamma = 0.6, type = "stochastic"),
    compute_n_errors(n = n, gamma = 0.2, type = "deterministic"),
    compute_n_errors(n = n, gamma = 0.4, type = "deterministic"),
    compute_n_errors(n = n, gamma = 0.6, type = "deterministic")
  )
  # Save for later use to avoid recomputing these
  write_rds(errors,file=here::here("errors.rds"), compress="xz", compression=9L)
}
```

```{r signif}
# Make STR the reference level for the statistical tests
errors <- errors %>%
       mutate(method = factor(method, c("STR","STL","TBATS")))
# Compute p-values
pvalues <- bind_rows(
    get_pvalues(errors, type="stochastic", gamma=0.2),
    get_pvalues(errors, type="stochastic", gamma=0.4),
    get_pvalues(errors, type="stochastic", gamma=0.6),
    get_pvalues(errors, type="deterministic", gamma=0.2),
    get_pvalues(errors, type="deterministic", gamma=0.4),
    get_pvalues(errors, type="deterministic", gamma=0.6)
  ) %>%
  mutate(method = str_remove(term,"method")) %>%
  select(-term) 
```

```{r cbetable}
# Table of RMSE values
rmse <- errors %>%
  group_by(type, gamma, method) %>%
  summarise(
    trend = sqrt(mean(trend^2)),
    season_week = sqrt(mean(season_week^2)),
    season_year = sqrt(mean(season_year^2)),
    remainder = sqrt(mean(remainder^2)),
  ) %>%
  ungroup()
rmse %>%
  pivot_longer(trend:remainder, names_to="var", values_to="rmse") %>%
  left_join(pvalues, by=c("type","gamma","method","var")) %>%
  mutate(
    method = factor(method, levels = c("STL","TBATS","STR")),
    rmse = sprintf("%.4f", rmse),
    rmse = if_else(p.value < 0.05, paste0("\\textbf{",rmse,"}"), rmse, missing=rmse)
  ) %>%
  pivot_wider(c(type,gamma,method),names_from="var",values_from="rmse") %>%
  arrange(type,gamma,method) %>%
  select(gamma, method, everything(), -type) %>%
  knitr::kable(
    col.names = c("$\\gamma$", "Method", "Trend RMSE", "Weekly RMSE", "Yearly RMSE", "Remainder RMSE"),
    caption = "RMSE over 100 simulations for each DGP and value of $\\gamma$. Bold values indicate results that are significantly different from the STR values.",
    digits = 3,
    escape = FALSE,
    align = "rlrrrr",
    booktabs = TRUE,
    format = "latex",
    table.envir = "table",
    position = "!ht"
  ) %>%
  kable_styling() %>%
  pack_rows("Stochastic DGP", 1, 9) %>%
  pack_rows("Deterministic GDP", 10, 18) %>%
  row_spec(seq(3, 15, by = 3), extra_latex_after = "\\midrule")
```

@@

We obtained similar results using other decomposition methods applied to the same data including STL [@cleveland1990stl], TBATS [@delivera2011forecasting] and X-13-ARIMA-SEATS [@findley2005some;@Dagum2016]. These comparisons are provided in the appendix.

@@

```{r vic, fig.height=10, fig.cap="Electricity demand in Victoria, decomposed using STR. The original data are plotted in black in the first panel, with the decomposed trend plotted in red. The subsequent panels contain the weekly seasonal pattern; the daily seasonal pattern with complex topology; the effect of temperature in Melbourne, which has a daily seasonal pattern with complex topology; the effect of squared temperatures in Melbourne, which is allowed to vary over time; and the residuals. Grey vertical lines represent the residuals with the largest absolute values.", dependson='outliers'}
elec_dbl <- elec %>%
  as_tsibble(index = DateTime) %>%
  mutate(
    Remainder = elec_str$output$random$data,
    Trend = predictor_dist(elec_str$output$predictors[[1]], 95),
    Weekly = predictor_dist(elec_str$output$predictors[[2]], 95),
    Daily = predictor_dist(elec_str$output$predictors[[3]], 95),
    Temp = predictor_dist(elec_str$output$predictors[[4]], 95),
    Tempsq = predictor_dist(elec_str$output$predictors[[5]], 95),
  ) %>%
  select(DateTime, Demand, Trend, Weekly, Daily, Temp, Tempsq, Remainder) %>%
  as_dable(
    response = "Demand",
    aliases = rlang::exprs(Demand = Trend + Weekly + Daily + Temp + Tempsq + Remainder),
    method = "STR"
  )
p <- elec_dbl %>%
  autoplot(size = 0.5, fill = "blue", level = 95) +
  xlab("Month") +
  geom_vline(data = outliers, aes(xintercept = DateTime), col = "gray") +
  ggplot2::theme_bw() + theme(legend.position = "none")
# Put vline behind data
p$layers <- p$layers[c(1, 4, 2, 3)]
p
```

@@

```{r outlierstable, results='asis'}
outliers %>%
  mutate(
    Hour1 = hour(DateTime),
    Hour2 = hour(DateTime + 1800),
    Minute1 = minute(DateTime) %>% as.character(),
    Minute2 = minute(DateTime + 1800) %>% as.character(),
    Minute1 = if_else(Minute1 == "0", "00", Minute1),
    Minute2 = if_else(Minute2 == "0", "00", Minute2),
    Time = paste0(Hour1, ":", Minute1, " -- ", Hour2, ":", Minute2),
    Weekday = case_when(
      Weekday == "Thu" ~ "Thursday",
      Weekday == "Fri" ~ "Friday"
    ),
    Date = paste(day(Date), month(Date, label = TRUE, abbr = FALSE), year(Date)),
  ) %>%
  select(Date, Weekday, Time, res) %>%
  knitr::kable(
    format='latex',
    col.names = c("Date", "Day of week", "Time period", "Residual"),
    digits = 1, align = "rlcr", booktabs = TRUE, linesep=10,
    position="!bh",
    caption = "The ten residuals that are largest in absolute value after an STR decomposition."
  )
```

```{r MelTemp, dependson='outliers', fig.height=3, fig.cap="The temperature in Melbourne on 1 February 2000, and the following ten days. Ten red lines (two groups of five lines each) mark the times of the outliers. The first group spans 14:30--17:00 on 3 February, while the second group spans 15:30--18:00 on the following day.", fig.pos="!bh"}
elec %>%
  filter(Date >= "2000-02-01", Date <= "2000-02-11") %>%
  ggplot(aes(x = DateTime, y = Temp)) +
  geom_line() +
  geom_vline(data = outliers, aes(xintercept = DateTime), col = "red") +
  labs(y = "Temperature", x = "Date") +
  ggplot2::theme_bw()
```

@@

Similarly, seasonal functional components can be obtained, using Fourier terms for example [reminiscent of @delivera2011forecasting]. This approach leads, with no additional effort, to handling seasonality with a fractional or varying period.

@@

## Feature engineering

The STR model provides a way to identify new features in time series data, such as weekly or daily patterns. These can then be used within other algorithms. For example, they could be used to classify time series [@catch22], to find anomalous time series (as distinct from anomalous observations) [@cikm2015], to select a forecasting model [@fforms], or to create a weighted forecast combination [@fforma].
